Thermodynamic response functions in a cell fluid model

### 2024-09-03 main_morse_response_functions.tex
extend introduction

	\section{The interaction potential}
	The potential of interaction between particles is taken in a form of a modified Morse potential
	\begin{equation}
		\label{def:mod_morse}
		U(r) = \varepsilon C_{H} \left[A {\rm e}^{-n_0(r-R_0)/\alpha} + {\rm e}^{-\gamma(r - R_0)/\alpha} -2{\rm e}^{-(r-R_0)/\alpha}\right],
	\end{equation}
	where $R_0$ is the coordinate of the potential minimum, $\alpha$ is an effective range of interaction, $\gamma$ and $n_0$ are parameters of the model. Other two constants $C_{H}$ and $A$ are expressed via $\gamma$ and $n_0$ as
	\begin{equation}
		C_{H} = \frac{n_0}{n_0 + \gamma - 2}, \quad A = \frac{2 - \gamma}{n_0},
	\end{equation}
	where $\varepsilon$ is the depth of the potential well at $r=R_0$. This potential is reduced to the ordinary Morse potential~\cite{Morse1929} at $\gamma=2$. For a more detailed discussion of such modified Morse potential, see Sections~1 and~2 in~\cite{KozlovskiiDobush2020}.

>>>>

	As the problem was considered in the framework of the grand canonical ensemble, the initial equation of state is formulated in terms of pressure $P$, temperature $T$ and the chemical potential $\mu$, $P = P(T,\mu)$. To leverage this form of the equation of state for calculation of the response functions, the corresponding definitions should be transformed to proper derivatives with respect to temperature and chemical potential~\cite{StrokerMeier2021}. For each response function considered in this paper, we present such transformation in a dedicated subsection. On the other hand, within the approach applied here, the chemical potential can be explicitly expressed via the number particle density $\rho$ and temperature. This gives rise to the equation of state in the form $P = P(T, \rho)$, in which case it is suitable to re-express the response functions in terms of derivatives with respect to temperature and density.

	In Section~\ref{sec:potential} we present the modified Morse potential used in our work, and briefly compare it with other possible modifications. Section~\ref{sec:eos} is dedicated to the explicit expressions for the equation of state. In Section~\ref{sec:respons_functions} the expressions for response functions are derived in terms of thermodynamic derivatives suitable for different forms of the equation of state.

	\section{\label{sec:potential}The interaction potential}
	The potential of interaction between particles is taken in a form of a modified Morse potential
	\begin{equation}
		\label{def:mod_morse}
		U(r) = \varepsilon C_{H} \left[A {\rm e}^{-n_0(r-R_0)/\alpha} + {\rm e}^{-\gamma(r - R_0)/\alpha} -2{\rm e}^{-(r-R_0)/\alpha}\right],
	\end{equation}
	where $R_0$ is the coordinate of the potential minimum, $\alpha$ is an effective range of interaction, $\gamma$ and $n_0$ are parameters of the model. Other two constants $C_{H}$ and $A$ are expressed via $\gamma$ and $n_0$ as
	\begin{equation}
		C_{H} = \frac{n_0}{n_0 + \gamma - 2}, \quad A = \frac{2 - \gamma}{n_0},
	\end{equation}
	where $\varepsilon$ is the depth of the potential well at $r=R_0$. This potential is reduced to the ordinary Morse potential~\cite{Morse1929} at $\gamma=2$. For a more detailed discussion of such modified Morse potential, see Sections~1 and~2 in~\cite{KozlovskiiDobush2020}.
